---
title: "Coursera Developing Data Products Week 3"
author: "Giovanni Madejski"
date: "January 12, 2018"
output: ioslides_presentation
---

````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
For this weeks assignment we are to create a webpage using R markdown that contains a plot made with Plotly. I am planing on visiting Zion National Park sometime this year and am interested in the monthly visitor data. The data for this project was found at https://www.nps.gov/zion/learn/management/park-visitation-statistics.htm. The data came in a pdf format so we did some initial transformation and cleaning of the data before loading the data into R.

## Loading and transforming data
```{r, echo = TRUE, warning=FALSE, message=FALSE}
library(reshape2)
library(plotly)
library(dplyr)
zion <- read.csv("ZION-VISITATION-2007-2017-8.csv", row.names = 1)
zion <- t(zion)
zion <- melt(zion)
colnames(zion)[] <- c("Month", "Year", "Visitors")
zion$Year <- as.factor(zion$Year)
```

## Creating the plot
```{r, echo= TRUE}
plot1 <- zion %>%
  plot_ly(x=~Month, y=~Visitors, color=~Year, type="scatter",
          mode = "lines+markers") %>%
  layout(title = "Monthly Visitors to Zion National Park 2007-2017")
```

## The plot
```{r,echo=FALSE, warning=FALSE}
plot1
```